### 2020-02-07 README.Rmd
Add experimental support for topic intrusion tests

@@

After the coding, you can look at the accuracy rate by printing the oolong test.

@@

>>>>

### Word intrusion test

@@

After the coding, you can look at the model precision by printing the oolong test.

@@

### Topic intrusion test

For example, `newsgroup_stm` was generated with the corpus `newsgroup5$text`

```{r newgroup5}
library(tibble)
newsgroup5
```

Create the oolong test object with the corpus used for training the topic model will generate topic intrusion test cases.

```{r createtest2}
oolong_test <- create_oolong(newsgroup_stm, newsgroup5$text)
oolong_test
```
